---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CRANE v1.0.0

Constrained Random Alteration of Network Edges (CRANE) is a computational method for sampling networks with fixed node strengths. This package also include CRANE integraction with ALPACA.

## Installation

You can install the released version of CRANE from [GitHub](https://github.com/PadiLab/CRANE) with:

``` r
library(devtools)
install_github("PadiLab/CRANE")
```

## Publication

**Generating Ensembles of Gene Regulatory Networks to Assess Robustness of Disease Modules**  
James T Lim, Chen Chen, Adam D Grant, Megha Padi  
bioRxiv 2020.07.12.198747; doi: https://doi.org/10.1101/2020.07.12.198747  
url: https://www.biorxiv.org/content/10.1101/2020.07.12.198747v1  

## Examples

We have included network edge list from angiogenic ovarian cancer (ang) and non-angiogenic ovarian cancer (nonAng). The following are some example use:

1. CRANE for network perturbation

```{r example1}
library(CRANE)
head(ang)

# Running CRANE for bipartite network
newElist=crane.bipartite(ang,alpha=0.3)

head(newElist)

```

2. CRANE integration with ALPACA
```{r example2}
library(ALPACA)
library(CRANE)

# Create Input Matrix nonAng as the baseline.
input=cbind(nonAng,ang[,3])

# Run ALPACA
alp=alpaca(input,NULL,verbose = F)

# Apply Crane
alpListObject=alpaca.crane(input, alp, isParallel = T)

# TF Results
head(alpListObject$TF)

# Gene Results
head(alpListObject$Gene)
```

```{r pressure, echo = FALSE}

```

